### 2023-04-13 chapter2/chapter2_supporting.tex
Added BM analysis supplement figures

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/root_variance.png}
\centering
\caption{\textbf{Variance ratios of disorder regions' feature roots.}
\textbf{(A)} Variance ratios before normalization. \textbf{(B)} Variance ratios after normalization. \textbf{(C)} Scree plot of the explained variance ratio by PC.}
\label{sfig:root_variance}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/rate_variance.png}
\centering
\caption{\textbf{Variance ratios of disorder regions' feature rates.}
\textbf{(A)} Variance ratios before normalization. \textbf{(B)} Variance ratios after normalization. \textbf{(C)} Scree plot of the explained variance ratio by PC.}
\label{sfig:rate_variance}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{brownian/out/order.png}
\centering
\caption{\textbf{PCA of order regions' feature rates.}
\textbf{(A)} The second and third PCs of the order regions' feature rate distributions. The explained variance percentage of each component is indicated in parentheses in the axis labels. \textbf{(B)} The same plot as panel B with the projections of original rates onto the components shown as arrows. Only the 16 features with the largest projections are shown. Scaling of the arrows is arbitrary.}
\label{sfig:order}
\end{figure}
